---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Let's unzip the ZIP file into current directory and load the data.
```{r unzip.n.load, echo=TRUE}
unzip('activity.zip')
activity <- read.csv('activity.csv',
                     colClasses=c('integer', 'Date', 'integer'))
```

## What is mean total number of steps taken per day?
We start the analysis by plotting an histogram of the number of steps by days. We will probably have a warning because of NAs.
```{r steps.by.day, echo=TRUE, message=FALSE}
library(dplyr)
library(ggplot2)

steps.by.day <- group_by(activity, date) %>%
  summarize(steps=sum(steps))

qplot(steps, data=steps.by.day, binwidth=1000) +
  xlab('Number of steps') +
  ylab('Number of days')
```

Let's glance at the mean and median values of the number of steps by day. They are surprisingly close.
```{r mean.and.median, echo=TRUE}
mean(steps.by.day$steps, na.rm=TRUE)
median(steps.by.day$steps, na.rm=TRUE)
```
## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
