---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Let's unzip the ZIP file into current directory and load the data.
```{r unzip.n.load, echo=TRUE}
unzip('activity.zip')
activity <- read.csv('activity.csv',
                     colClasses=c('integer', 'Date', 'integer'))
```

## What is mean total number of steps taken per day?
We start the analysis by plotting an histogram of the number of steps by days. We will probably have a warning because of NAs.
```{r steps.by.day, echo=TRUE, message=FALSE}
library(dplyr)
library(scales)
library(ggplot2)

steps.by.day <- group_by(activity, date) %>%
  summarize(steps=sum(steps))

qplot(steps, data=steps.by.day, binwidth=1000) +
  xlab('Number of steps') +
  ylab('Number of days') +
  geom_rug()
```

Let's glance at the mean and median values of the number of steps by day. They are surprisingly close.
```{r mean.and.median, echo=TRUE}
mean(steps.by.day$steps, na.rm=TRUE)
median(steps.by.day$steps, na.rm=TRUE)
```

## What is the average daily activity pattern?
```{r steps.by.interval, echo=TRUE}
steps.by.interval <- group_by(activity, interval) %>%
  summarize(steps=mean(steps, na.rm=TRUE)) %>%
  mutate(time=ISOdate(2015, 4, 20, floor(interval / 100), interval %% 100))
# Added a random date (actually the assignement due date) with the time
# corresponding to the interval. Will make a nicer plot ;)

qplot(time, steps, data=steps.by.interval, geom='line') +
  scale_x_datetime(labels=date_format("%H:%M"), breaks="2 hours")
```

Well this looks OK. There are a few occasional steps between 11PM and 5AM, but otherwise it looks like a good nap time.

Now let's find the most active interval that looks like it's around 8:30.
```{r max_steps.by.interval}
filter(steps.by.interval, steps==max(steps)) %>% select(-time)
```

And it is the interval from 8:35 to 8:40 indeed, with an average of a bit more than 200 steps.

## Imputing missing values
How many missing values in the dataset ?
```{r missing.nb, echo=TRUE}
sum(is.na(activity$steps))
nrow(activity)
sum(is.na(activity$steps)) / nrow(activity)
```

There are 2304 missing values, out of 17,568. That is about 13%.

Let's remplace NAs with mean for the corresponding 5 minutes interval.
```{r activity.imputed, echo=TRUE}
activity.imputed <- group_by(activity, interval) %>%
  mutate(steps=ifelse(is.na(steps), mean(steps, na.rm=TRUE), steps)) %>%
  ungroup

steps.by.day.imputed <- group_by(activity.imputed, date) %>%
  summarize(steps=sum(steps))

qplot(steps, data=steps.by.day.imputed, binwidth=1000) +
  xlab('Number of steps') +
  ylab('Number of days') +
  geom_rug()
```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
# It's probably better to use the POSIXlt $wday than the weekdays method
# to avoid locale issues
activity.imputed$weekday <- ifelse(
  strptime(activity.imputed$date, "%F")$wday %in% 1:5,
  "weekday",
  "weekend")

steps.by.interval.imputed <- group_by(activity.imputed, interval, weekday) %>%
  summarize(steps=mean(steps, na.rm=TRUE)) %>%
  mutate(time=ISOdate(2015, 4, 20, floor(interval / 100), interval %% 100))
# Added a random date (actually the assignement due date) with the time
# corresponding to the interval. Will make a nicer plot ;)

qplot(time, steps, data=steps.by.interval.imputed, geom='line') +
  scale_x_datetime(labels=date_format("%H:%M"), breaks="2 hours") +
  facet_grid(weekday ~ .)
```
